---
title: "Title"
subtitle: "Subtitle"  
author: "Lars Schoebitz"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["xaringan-themer.css", "my-css-style.css"]
    seal: FALSE
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}

options(htmltools.dir.version = FALSE)

library(tidyverse)
library(readr)
library(tmap)
library(grDevices)
library(htmltools)

library(xaringanthemer)
library(paletteer)

# paletteer_d("dutchmasters::milkmaid", n = 5)
# paletteer_d("colorblindr::OkabeIto", n = 8)

knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE,
  fig.height = 6, fig.width = 12 
)

```

```{r xaringan-themer, include=FALSE, warning=FALSE}

style_mono_accent(
  base_color = "#0F4C81", # Pantone Classic Blue
  header_font_google = google_font("Montserrat"),
  code_font_google = google_font("Fira Mono"),
  text_font_size = "1.4rem",
  footnote_font_size = "0.8rem",
  footnote_position_bottom = "20px",
  header_background_padding = "2rem"
)

```



```{r}

url = "https://github.com/larnsce/sanitation_data/raw/master/data/derived_data/2020-09-03_jmp_sanitation_raw_data.rds"

download.file(url, destfile = here::here("data/2020-09-03_jmp_sanitation_raw_data.rds"))

jmpraw <- read_rds(here::here("data/2020-09-03_jmp_sanitation_raw_data.rds"))

```

```{r}

# data manipulation

## ww treatment

ww_treatment <- jmpraw %>% 
  filter(!is.na(san_service_chain)) %>%
  filter(
    san_service_chain == "WW treatment"
  ) %>% 
  group_by(iso3, san_service_chain) %>% 
  count()

## fs treatment

fs_treatment <- jmpraw %>% 
  filter(!is.na(san_service_chain)) %>%
  filter(
    san_service_chain == "FS treatment"
  ) %>% 
  group_by(iso3, san_service_chain) %>% 
  count()

```

```{r}

# world map data

data("World")

world_ww_treatment <- World %>% 
  left_join(ww_treatment, by = c("iso_a3" = "iso3")) %>% 
  filter(continent != "Antarctica") 

world_fs_treatment <- World %>% 
  left_join(fs_treatment, by = c("iso_a3" = "iso3")) %>% 
  filter(continent != "Antarctica")

```

class: title-slide

## The 6.2 Data Gap
### What's the gap we are talking about?

.bottom[

```{r, echo=FALSE}
p("Lars Schöbitz")
p("Prepared for UN World Data Forum")
p("October, 2020")
```
]

---

```{r, fig.showtext = TRUE, fig.width=15, fig.height=8}

## figure 1

p1 <- jmpraw %>% 
  filter(!is.na(san_service_chain)) %>% 
  group_by(san_service_chain) %>% 
  filter(san_service_chain != "sharing") %>% 
  count() %>% 
  
  ## plot
  
  ggplot(aes(x = forcats::fct_rev(san_service_chain), y = n)) +
  geom_col() +
  labs(
    title = "Number of data points along sanitation service chain",
    subtitle = "For 232 countries; since 1995",
    y = "Data points",
    x = "Sanitation Service Chain", 
    caption = "Data source: washdata.org" 
  ) +
  coord_flip() +
  theme_minimal() +
  scale_y_continuous(breaks = seq(0, 9000, 1000)) +
  theme_xaringan(background_color = "#FFFFFF") +
  scale_xaringan_fill_discrete() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor.y = element_blank()
    ) 
  

p1

```


---

```{r, fig.showtext = TRUE, fig.width=15, fig.height=8}
p1 +
  annotate("text", x = 4, y = 1000, label = "388", size = 7) +
  annotate("text", x = 3, y = 300, label = "7", size = 7) +
  annotate("text", x = 2, y = 500, label = "58", size = 7) +
  annotate("text", x = 1, y = 1300, label = "756", size = 7) 


```

---
## Wastewater Treatment

```{r, fig.showtext = TRUE, fig.width=15, fig.height=8}

tmap_mode("plot")

tm_shape(world_ww_treatment) +
  tm_polygons(
    col = "n", 
    title = "No. of data points", 
    palette = "Blues", 
    n = 3, 
    textNA = "No Data",
    colorNA = "grey30", 
    lwd = 0.5
    ) +
  tm_layout(
    scale = 3,
    inner.margins = c(0, .02, .02, .02),
    outer.margins = c(0, 0, 0, 0), frame = FALSE, 
    ) 

```

---
## Faecal Sludge Treatment

```{r, fig.showtext = TRUE, fig.width=15, fig.height=7}

tmap_mode("view")
tmap_options(basemaps = "OpenStreetMap")

map_fs <- tm_shape(select(world_fs_treatment, -iso_a3)) +
  tm_polygons(
    col = "n", 
    title = "No. of data points", 
    palette = "Blues", 
    n = 2, 
    textNA = "No Data",
    colorNA = "grey30", 
    lwd = 0.5
    ) +
  tm_layout(
    scale = 3,
    inner.margins = c(0, .02, .02, .02),
    outer.margins = c(0, 0, 0, 0), frame = FALSE, 
    ) 

map_fs +
  tm_view(set.view = 2) 


```

---
## References

Slides created via the R package [{xaringan}](https://github.com/yihui/xaringan) and [{xaringanthemer}](https://github.com/gadenbuie/xaringanthemer). 

Raw data is obtained from washdata.org. Source code and tidy data table for plots in these slides can be accessed from the R Package [{WASHdata}](https://github.com/larnsce/sanitation_data).

Source code for slides is accessible from GitHub repository [UNWDF-session](https://github.com/larnsce/UNWDF-session). The material is licensed under the [MIT License](https://github.com/larnsce/UNWDF-session/blob/master/LICENSE).
